CS6735 Programming Assignment

### 2017-12-11 cs6735/assignment/report.tex
updating accuracies
preparing submission

\title{Generative Adversarial Networks}
\author{Jacob Smith}
\date{December 12, 2017}

@@

Initially, the weights are set to $\frac{1}{|S|}$. For a predefined number of iterations, a weak learner is trained on the a subset of the training data. Predictions are made for each training sample and the error is calculated. Using the accuracy, a value $\alpha$ is calculated which represents the accuracy of the weak learner. This $\alpha$ value is used to update the weights and the weak learner, $\alpha$ pair is added to the list of previous weak learners. To make classification, there is a weighted vote between using the weak learners and their associated $\alpha$ values and the sign is used to make the final classification.

@@

\subsection{ID3}
\begin{tabular}{ |c|c| } \hline
  \bb{Dataset}       & \bb{Minimum \# of Samples} \\ \hline
  Breast Cancer      & 1                          \\ \hline
  Car                & 1                          \\ \hline
  E. Coli            & 2                          \\ \hline
  Letter Recognition & 1                          \\ \hline
  Mushroom           & 1                          \\ \hline
\end{tabular}

\subsection{Naïve Bayes}
\begin{tabular}{ |c|c| } \hline
  \bb{Dataset}       & \bb{Distribution} \\ \hline
  Breast Cancer      & None              \\ \hline
  Car                & None              \\ \hline
  E. Coli            & Gaussian          \\ \hline
  Letter Recognition & Gaussian          \\ \hline
  Mushroom           & None              \\ \hline
\end{tabular}

\subsection{AdaBoost on ID3}
\begin{tabular}{ |c|c|c|c| } \hline
  \bb{Dataset}       & \bb{Max Level} & \bb{\# of Learners} & Proportion of Samples \\ \hline
  Breast Cancer      & 1              & 100                 & 0.50                  \\ \hline
  Car                & 1              & 100                 & 0.70                  \\ \hline
  E. Coli            & 1              & 100                 & 0.50                  \\ \hline
  Letter Recognition & 1              & IDK                 & IDK                   \\ \hline
  Mushroom           & 1              & 10                  & 0.30                  \\ \hline
\end{tabular}

\subsection{AdaBoost on Naïve Bayes}
\begin{tabular}{ |c|c|c|c| } \hline
  \bb{Dataset}       & \bb{Distribution} & \bb{\# of Learners} & Proportion of Samples \\ \hline
  Breast Cancer      & None              & 100                 & 0.70                  \\ \hline
  Car                & None              & 100                 & 0.40                  \\ \hline
  E. Coli            & Gaussian          & 150                 & 0.30                  \\ \hline
  Letter Recognition & Gaussian          & IDK                 & IDK                   \\ \hline
  Mushroom           & None              & 10                  & 0.30                  \\ \hline
\end{tabular}

\subsection{Random Forest}
\begin{tabular}{ |c|c|c| } \hline
  \bb{Dataset}       & \bb{\# of Learners} & Proportion of Samples \\ \hline
  Breast Cancer      & 120                 & 0.70                  \\ \hline
  Car                & 200                 & 0.60                  \\ \hline
  E. Coli            & 120                 & 0.70                  \\ \hline
  Letter Recognition & 50                  & 0.30                  \\ \hline
  Mushroom           & 10                  & 0.30                  \\ \hline
\end{tabular}

\subsection{K-Nearest Neighbors}
\begin{tabular}{ |c|c|c| } \hline
  \bb{Dataset}       & \bb{K} & Distance  \\ \hline
  Breast Cancer      & 1      & Hamming   \\ \hline
  Car                & 1      & Hamming   \\ \hline
  E. Coli            & 1      & Euclidian \\ \hline
  Letter Recognition & 1      & Euclidian \\ \hline
  Mushroom           & 1      & Hamming   \\ \hline
\end{tabular}

@@

\section{Results}
\begin{table}
  \begin{tabular}{ |c|c|c|c|c|c| }
    \hline
    \bb{Algorithm}               & \bb{Breast Cancer} & \bb{Car} & \bb{Letter} & \bb{E. Coli}  & \bb{Mushroom} \\ \hline
    \bb{ID3}                     & 97.994\%           & 90.634\% & 87.930\%    & 79.678\%      & 99.998\%      \\ \hline
    \bb{Naïve Bayes}             & 97.663\%           & 81.940\% & 64.570\%    & 80.556\%      & 95.952\%      \\ \hline
    \bb{AdaBoost on ID3}         & 98.715\%           & 88.822\% & 96.125\%    & 84.460\%      & 99.446\%      \\ \hline
    \bb{AdaBoost on Naïve Bayes} & 98.626\%           & 91.367\% & 56.960\%    & 78.803\%      & 99.744\%      \\ \hline
    \bb{Random Forest}           & 97.592\%           & 91.175\% & 91.949\%    & 84.021\%      & 99.865\%      \\ \hline
    \bb{K-Nearest Neighbors}     & 98.050\%           & 89.763\% & 93.923\%    & 87.779\%      & 99.826\%      \\ \hline
  \end{tabular}
  \caption{Accuracy of the six implemented algorithms on five UCI Machine Learning repositories. Results calculated using 10 times 5-fold cross validation.}
  \label{table:accuracies}
\end{table}

\begin{table}
  \begin{tabular}{ |c|c|c|c|c|c| }
    \hline
    \bb{Algorithm}               & \bb{Breast Cancer} & \bb{Car} & \bb{Letter} & \bb{E. Coli}  & \bb{Mushroom} \\ \hline
    \bb{ID3}                     & 1.465\%            & 4.061\%  & 3.392\%     & 8.952\%       & 0.017\%       \\ \hline
    \bb{Naïve Bayes}             & 1.678\%            & 3.373\%  & 1.357\%     & 11.199\%      & 2.128\%       \\ \hline
    \bb{AdaBoost on ID3}         & 1.216\%            & 3.085\%  & 1.066\%     & 8.246\%       & 1.081\%       \\ \hline
    \bb{AdaBoost on Naïve Bayes} & 1.394\%            & 1.987\%  & 1.780\%     & 8.802\%       & 0.652\%       \\ \hline
    \bb{Random Forest}           & 1.597\%            & 5.171\%  & 2.622\%     & 8.325\%       & 0.702\%       \\ \hline
    \bb{K-Nearest Neighbors}     & 1.118\%            & 3.967\%  & 2.284\%     & 8.089\%       & 0.433\%       \\ \hline
  \end{tabular}
  \caption{Standard deviation of the six implemented algorithms on five UCI Machine Learning repositories. Results calculated using 10 times 5-fold cross validation.}
\end{table}

>>>>

\title{CS6735 Programming Assignment}
\author{Jacob Smith}
\date{December 12, 2017}

@@

Initially, the weights are set to $\frac{1}{|S|}$. For a predefined number of iterations, a new weak learner is trained on the a subset of the training data. Predictions are made for each training sample and the error is calculated. Using the accuracy, a value $\alpha$ is calculated which represents the accuracy of the weak learner. This $\alpha$ value is used to update the weights and the weak learner, $\alpha$ pair is added to the list of previous weak learners. To make classification, there is a weighted vote between using the weak learners and their associated $\alpha$ values and the sign is used to make the final classification.

@@

\subsection{ID3}
\begin{tabular}{ |c|c| } \hline
  \bb{Dataset}            & \bb{Minimum \# of Samples} \\ \hline
  \bb{Breast Cancer}      & 1                          \\ \hline
  \bb{Car}                & 1                          \\ \hline
  \bb{E. Coli}            & 2                          \\ \hline
  \bb{Letter Recognition} & 1                          \\ \hline
  \bb{Mushroom}           & 1                          \\ \hline
\end{tabular}

\subsection{Naïve Bayes}
\begin{tabular}{ |c|c| } \hline
  \bb{Dataset}            & \bb{Distribution} \\ \hline
  \bb{Breast Cancer}      & None              \\ \hline
  \bb{Car}                & None              \\ \hline
  \bb{E. Coli}            & Gaussian          \\ \hline
  \bb{Letter Recognition} & Gaussian          \\ \hline
  \bb{Mushroom}           & None              \\ \hline
\end{tabular}

\subsection{AdaBoost on ID3}
\begin{tabular}{ |c|c|c|c| } \hline
  \bb{Dataset}            & \bb{Max Level} & \bb{\# of Learners} & \bb{Proportion of Samples} \\ \hline
  \bb{Breast Cancer}      & 1              & 100                 & 0.50                       \\ \hline
  \bb{Car}                & 4              & 200                 & 0.30                       \\ \hline
  \bb{E. Coli}            & 3              & 100                 & 0.20                       \\ \hline
  \bb{Letter Recognition} & 8              & 300                 & 0.25                       \\ \hline
  \bb{Mushroom}           & 3              & 10                  & 0.30                       \\ \hline
\end{tabular}

\subsection{AdaBoost on Naïve Bayes}
\begin{tabular}{ |c|c|c|c| } \hline
  \bb{Dataset}            & \bb{Distribution} & \bb{\# of Learners} & \bb{Proportion of Samples} \\ \hline
  \bb{Breast Cancer}      & None              & 100                 & 0.70                       \\ \hline
  \bb{Car}                & None              & 100                 & 0.40                       \\ \hline
  \bb{E. Coli}            & Gaussian          & 250                 & 0.10                       \\ \hline
  \bb{Letter Recognition} & Gaussian          & 10                  & 0.30                       \\ \hline
  \bb{Mushroom}           & None              & 10                  & 0.50                       \\ \hline
\end{tabular}

\subsection{Random Forest}
\begin{tabular}{ |c|c|c| } \hline
  \bb{Dataset}            & \bb{\# of Learners} & \bb{Proportion of Samples} \\ \hline
  \bb{Breast Cancer}      & 120                 & 0.70                       \\ \hline
  \bb{Car}                & 200                 & 0.60                       \\ \hline
  \bb{E. Coli}            & 250                 & 0.60                       \\ \hline
  \bb{Letter Recognition} & 100                 & 0.60                       \\ \hline
  \bb{Mushroom}           & 10                  & 0.50                       \\ \hline
\end{tabular}

\subsection{K-Nearest Neighbors}
\begin{tabular}{ |c|c|c| } \hline
  \bb{Dataset}            & \bb{K} & Distance  \\ \hline
  \bb{Breast Cancer}      & 1      & Hamming   \\ \hline
  \bb{Car}                & 1      & Hamming   \\ \hline
  \bb{E. Coli}            & 1      & Euclidian \\ \hline
  \bb{Letter Recognition} & 1      & Euclidian \\ \hline
  \bb{Mushroom}           & 1      & Hamming   \\ \hline
\end{tabular}

@@

\section{Results}
\begin{table} [!htbp]
  \begin{tabular}{ |c|c|c|c|c|c| }
    \hline
    \bb{Algorithm}               & \bb{Breast Cancer} & \bb{Car} & \bb{Letter} & \bb{E. Coli}  & \bb{Mushroom} \\ \hline
    \bb{ID3}                     & 97.994\%           & 90.634\% & 87.930\%    & 79.678\%      & 99.998\%      \\ \hline
    \bb{Naïve Bayes}             & 97.663\%           & 81.940\% & 64.570\%    & 80.556\%      & 95.952\%      \\ \hline
    \bb{AdaBoost on ID3}         & 98.715\%           & 93.295\% & 97.050\%    & 86.918\%      & 99.828\%      \\ \hline
    \bb{AdaBoost on Naïve Bayes} & 98.626\%           & 91.367\% & 59.540\%    & 78.803\%      & 99.744\%      \\ \hline
    \bb{Random Forest}           & 98.585\%           & 91.175\% & 93.120\%    & 84.021\%      & 99.865\%      \\ \hline
    \bb{K-Nearest Neighbors}     & 98.050\%           & 89.763\% & 93.923\%    & 87.779\%      & 99.826\%      \\ \hline
  \end{tabular}
  \caption{Accuracy of the six implemented algorithms on five UCI Machine Learning repositories. Results calculated using 10 times 5-fold cross validation.}
  \label{table:accuracies}
\end{table}

\begin{table} [!htbp]
  \begin{tabular}{ |c|c|c|c|c|c| }
    \hline
    \bb{Algorithm}               & \bb{Breast Cancer} & \bb{Car} & \bb{Letter} & \bb{E. Coli}  & \bb{Mushroom} \\ \hline
    \bb{ID3}                     & 1.465\%            & 4.061\%  & 3.392\%     & 8.952\%       & 0.017\%       \\ \hline
    \bb{Naïve Bayes}             & 1.678\%            & 3.373\%  & 1.357\%     & 11.199\%      & 2.128\%       \\ \hline
    \bb{AdaBoost on ID3}         & 1.216\%            & 3.143\%  & 0.989\%     & 6.908\%       & 0.293\%       \\ \hline
    \bb{AdaBoost on Naïve Bayes} & 1.394\%            & 1.987\%  & 0.716\%     & 8.802\%       & 0.652\%       \\ \hline
    \bb{Random Forest}           & 1.597\%            & 5.171\%  & 2.622\%     & 8.325\%       & 0.702\%       \\ \hline
    \bb{K-Nearest Neighbors}     & 1.118\%            & 3.967\%  & 2.284\%     & 8.089\%       & 0.433\%       \\ \hline
  \end{tabular}
  \caption{Standard deviation of the six implemented algorithms on five UCI Machine Learning repositories. Results calculated using 10 times 5-fold cross validation.}
\end{table}
